---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# AIMEE

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/jonahcullen/AIMEE/workflows/R-CMD-check/badge.svg)](https://github.com/jonahcullen/AIMEE/actions)
<!-- badges: end -->

AIMEE (Animal IsomiR and MiRNA Expression Explorer) hosts miRNA and isomiR expression data across 461 equine small RNA-seq samples, spanning 61 tissue types. The samples were sourced from 12 American Quarter horses, 4 FAANG Thoroughbreds, and 158 samples from public data repositories. All samples were processed using the pipeline FARmiR (https://github.com/jonahcullen/FARmiR).

## Installation

You can install the development version of AIMEE like so:

``` r
# install devtools if you have not already
install.packages("devtools")

# install package from github
devtools::install_github("jonahcullen/AIMEE")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(AIMEE)
run_app()
## basic example code
```

## Code of Conduct

Please note that the AIMEE project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
